### 2016-05-24 intro.tex
I guess it is not a counterxample after all
beginning to craft a proper intro to the paper

\section{Introduction}
\paragraph{Basic issues in Naor-Yogev. }
\begin{itemize}
\item The NY paper formalizes and investigates a security notion of limited interest
\item The proposed construction won't scale in common network applications (e.g. large CDN, P2P networks)
\item The main (im)possibility results are of theoretical interest only
\item The basic syntax and operation of their Bloom filter formalization is underdefined.  (This really irritates me.)  It isn’t clear that their Bloom filter formalization actually captures traditional Bloom filters! \tsnote{UPDATE (5/20/16): It is clear, now, that it \emph{does not}.} \tsnote{Also, why isn't the size of the representation somehow a part of the syntax or correctness/soundness conditions?  The fact that the representation is supposed to be small doesn't appear in the syntax anywhere so, syntactically, $B_1(S)=S$ and $B_2(S,x)=1 \Leftrightarrow x \in S$ works just fine, and is trivially secure by their definition!  In fact, I think this contradicts their main claim that secure ``Bloom filters'' exist iff one-way functions exist :-)}
\item The ``adversarial-resilient Bloom Filter'' definition does not give the adversary access to the hash functions that created the representation; effectively, they are secret. (No matter if the [NY] syntax does or does not allow them to be encoded in the representation.)  This is odd and does not match reality, e.g. the popular Squid proxy uses plain MD5, splits the output into four chunks, and defines these as four hash functions.  Hardly secret. \tsnote{I did find a setting where Bloom filters use secret keys: privacy-preserving record linkage.  Here one wants to know if two databases contain information about the same person (abstractly, a set of record identifiers); you create a Bloom filter for each record, one for each unique identifier in some cases.  Suggested hash functions are $H_j(x) = g(x) + j\cdot h(x) \bmod m$ for $j=\{0,1,\ldots,k-1\}$, and $g,h$ are (e.g.) HMAC-SHA1 with different keys.  In practice, apparently the~$x$ are bigrams extracted from string identifiers (e.g. ``Thomas''); papers show how to break this ``encrypted'' Bloom filter by recovering a large fraction of names, via (roughly) frequency analysis.}
\item The ``unsteady representation'' does not seem well founded.  Not sure what Bloom filter-like data structures would have randomized querying procedures.  They mention the possibility of differential privacy mechanisms being incorporated into the querying procedure.  But what's the purpose of this, if the security definition gives the adversary the set~$S$?  (What are you keeping private?) 
\end{itemize}

@@

>>>>

\section{Introduction}
We revisit the formalization of Bloom filters~\cite{xxx} and closely related data structures as primitives with explicit security goals.  Recently, Naor and Yogev~\cite{xxx} (hereafter NY) gave such a formalization, providing syntax for a generalized abstraction of Bloom filters, as well as casting the classical Bloom filter soundness condition as a security experiment admiting adaptive adversaries.  To briefly summarize, a Bloom filter is a data structure for compactly representing a set~$\mathcal{S}$ in a way that supports constant time responses to set-membership queries.  The representation of~$\mathcal{S}$ is an indexed array~$M$ of~$m$-bits, all initally set to 0.  To insert $x \in \mathcal{S}$ into~$M$, one computes indices $h_1(x),h_2(x),\ldots,h_k(x)$ where each $h_i \colon \mathcal{U} \to \{0,1,\ldots m-1\}$ maps from a universe~$\mathcal{U}$ (which contains $\mathcal{S}$) to indices of~$M$.  The bits at positions $h_1(x),h_2(x),\ldots,h_k(x)$ are set to 1; if a bit is already 1, due to inserting some previous element of~$\mathcal{S}$, then it is left alone.  After all elements of~$\mathcal{S}$ have been inserted, the resulting bit-array~$M$ is taken as the representation.  To test if $y \in \mathcal{S}$, one checks if  $(h_1(y)=1 \wedge h_2(y)=1 \wedge \cdots \wedge h_k(y)=1)$, returning ``yes'' if so, and ``no'' otherwise.   Bloom filters are correct, in the sense that if $y \in \mathcal{S}$, the set-membership test always returns ``yes''.  The classical soundness condition asserts that for all $y \notin\mathcal{S}$,  $\Prob{h_1,h_2,\ldots,h_k \getsr \mathrm{Func(\mathcal{U},\mathbb{Z}_m)}\colon h_1(y)=1 \wedge h_2(y)=1 \wedge \cdots \wedge h_k(y)=1} \leq \epsilon$ where $\epsilon$, the false-positive rate, is a parameter of the Bloom filter.  (The values of~$\epsilon,m,k,|\mathcal{S}|$ are related in a well known way.)  NY recast this soundness condition as a game in which an adversary~$A$ is given~$\mathcal{S}$ and an oracle for set-membership queries, and it attempts to find a false-positive.  The fact that~$A$ can \emph{adapt} its queries and its output based on what it learns from the set-membership oracle is the key definitional constribution of NY.

\if{0}
\paragraph{Basic issues in Naor-Yogev. }
\begin{itemize}
\item The NY paper formalizes and investigates a security notion of limited interest
\item The proposed construction won't scale in common network applications (e.g. large CDN, P2P networks)
\item The main (im)possibility results are of theoretical interest only
\item The basic syntax and operation of their Bloom filter formalization is underdefined.  (This really irritates me.)  It isn’t clear that their Bloom filter formalization actually captures traditional Bloom filters! \tsnote{UPDATE (5/20/16): It is clear, now, that it \emph{does not}.} \tsnote{Also, why isn't the size of the representation somehow a part of the syntax or correctness/soundness conditions?  The fact that the representation is supposed to be small doesn't appear in the syntax anywhere so, syntactically, $B_1(S)=S$ and $B_2(S,x)=1 \Leftrightarrow x \in S$ works just fine, and is trivially secure by their definition! }
\item The ``adversarial-resilient Bloom Filter'' definition does not give the adversary access to the hash functions that created the representation; effectively, they are secret. (No matter if the [NY] syntax does or does not allow them to be encoded in the representation.)  This is odd and does not match reality, e.g. the popular Squid proxy uses plain MD5, splits the output into four chunks, and defines these as four hash functions.  Hardly secret. \tsnote{I did find a setting where Bloom filters use secret keys: privacy-preserving record linkage.  Here one wants to know if two databases contain information about the same person (abstractly, a set of record identifiers); you create a Bloom filter for each record, one for each unique identifier in some cases.  Suggested hash functions are $H_j(x) = g(x) + j\cdot h(x) \bmod m$ for $j=\{0,1,\ldots,k-1\}$, and $g,h$ are (e.g.) HMAC-SHA1 with different keys.  In practice, apparently the~$x$ are bigrams extracted from string identifiers (e.g. ``Thomas''); papers show how to break this ``encrypted'' Bloom filter by recovering a large fraction of names, via (roughly) frequency analysis.}
\item The ``unsteady representation'' does not seem well founded.  Not sure what Bloom filter-like data structures would have randomized querying procedures.  They mention the possibility of differential privacy mechanisms being incorporated into the querying procedure.  But what's the purpose of this, if the security definition gives the adversary the set~$S$?  (What are you keeping private?) 
\end{itemize}

@@

\fi
